The state of knowledge for marine invertebrate biodiversity in the continental US

### 2017-06-14 manuscript.Rmd
[fix #22] incorporate Mark's comments

Museum collections have been recording our knowledge about species and their geographic ranges, but until recently, this information was fragmented across institutions and difficult to synthesize. The digitization of natural history collections and other biodiversity information systems can now be used to enable synthesis and highlight knowledge gaps. Here we use these data to synthesize the state of our knowledge for marine invertebrates in the continental US. We show that current knowledge and sampling efforts are inadequate given the diversity of the fauna and the geographic extent of US. While recent high-throughput sequencing technologies promise to greatly speed up the documentation of marine species and their ranges, its value would be greatly improved by anchoring the results into existing DNA sequence data and associated voucher. However, the best documented phyla have at most 25% of their species sequenced for COI. More sampling, coordinated at the scale of the US, is needed to improve our knowledge of species and their geographic ranges. This data is needed to detect the impact of global change and other perturbations. Advances in computing, information systems, and sequencing technologies, have set the stage to inform where future efforts for documenting biodiversity should be applied.

@@

With increasing impact of human activities on the biosphere, we need efficient and accurate approaches to document changes in species ranges and community composition. While terrestrial ecosystems have received considerable attention, the baseline of healthy and resilient marine ecosystems are not well understood [@Worm2006], and modeling the impact of human activities is limited to a few taxonomic groups [@Tittensor2010]. A major hindrance for marine species, is that we do not have enough information about which species live where, and an unknown but potentially significant portion of marine biodiversity remains to be discovered and described [@Mora2011]. Additionally, coordinated marine ecosystem monitoring initiatives are lacking [@Duffy2013,@Borja2016]. There is therefore a pressing need to improve our knowledge of marine systems before species go extinct, and their functioning is irreversibly altered.

Until very recently, our knowledge of biodiversity was scattered among heterogeneous sources (e.g. natural history collections, publications, expert knowledge), difficult to access, and therefore difficult to synthesize. The development of public databases for natural history records (e.g. iDigBio [@Page2015]), species occurrences (e.g., OBIS [@Zhang2002]), genetic data (e.g., GenBank [@Benson2013], BOLD [@Ratnasingham2007a]), and registers of species names (e.g., WoRMS [@Costello2013b]), now allow us to evaluate what and how much we know. Here, we aggregate publicly available data for marine invertebrates that occur in the continental United States, the Gulf of Mexico, and the Pacific Northwest, to highlight gaps in our knowledge. We show that public databases are relatively incomplete, and that most species are known from only a few specimens and a few locations. We emphasize that our understanding of marine biodiversity, and the impact of human activities on communities require not only to get a more accurate list of the species that inhabits the oceans, but we also need more comprehensive data on species distributions and abundances. This can only be achieved with additional sampling and a commitment to training more taxonomists and experts that can identify the material collected.

@@

To compare the faunistic lists from the Gulf of Mexico and the Pacific Northwest with records in public databases, we queried the iDigBio and OBIS databases for all records they included in the same geographic boundaries as the lists. After filtering these lists to only include the same higher taxonomic level taxa as the species lists, and keeping only records for which the species could be matched to a species name in WoRMS, we had for the Gulf of Mexico `r nrow(idigbio_gom_records)` and `r nrow(obis_gom_records)` records for iDigBio and OBIS respectively, representing `r dplyr::n_distinct(idigbio_gom_records$worms_valid_name)` and `r dplyr::n_distinct(obis_gom_records$worms_valid_name)` species. For the Pacific Northwest, we retrieved `r nrow(idigbio_pnw_records)` and `r nrow(obis_kozloff_records)` records for iDigBio and OBIS respectively representing `r dplyr::n_distinct(idigbio_pnw_records$worms_valid_name)` and `r dplyr::n_distinct(obis_kozloff_records$worms_valid_name)` species. For the Gulf of Mexico, the majority of the species included in the expert lists are recorded in both iDigBio and OBIS (`r format_output(species_in_common$n_spp_gom_idigbio_obis/species_in_common$n_spp_gom*100)` %), or only OBIS (`r format_output(species_in_common$n_spp_gom_obis/species_in_common$n_spp_gom*100)` %) (Fig. \@ref(fig:database-overlap)). For the Pacific Northwest, these proportions were much lower with only `r format_output(species_in_common$n_spp_kozloff_idigbio_obis/species_in_common$n_spp_kozloff*100)`% of the species from the regional list with records in OBIS and iDigBio, and `r format_output(species_in_common$n_spp_kozloff_obis/species_in_common$n_spp_kozloff*100)`%  in OBIS only (Fig. \@ref(fig:database-coverage)).

```{r compare_database_coverage, fig.cap='Overlap between the regional species list (list), records in iDigBio (idigbio), records in OBIS (obis), and records in BOLD (bold) for the Gulf of Mexico (left) and the Pacific Northwest (right). (\\#fig:database-overlap)', echo=FALSE}
knitr::include_graphics("figures/database_coverage.pdf")
```

@@

We extracted `r sum(gom_worms$is_marine, na.rm = TRUE)` marine invertebrates species from the faunistic list of the Gulf of Mexico, and `r sum(kozloff_worms$is_marine, na.rm=TRUE)` species from the Salish Sea. We then looked for the number of species listed that are known to occur in the same geographic area, the United States, or anywhere else in the world. Overall, OBIS had georeferenced records for most of the species that are included in the species lists. However, even for the better studied phyla about 75% of the species have records from the same geographic area, while it is less than 50% for the Pacific Northwest.

@@

These results suggest that even when considering species lists that have been curated and that represent possibly the most accurate knowledge for this geographic area, today we could only reconstruct these lists partially based on digitized information. For instance, based on OBIS data the list would be `r format_output(summary_richness_per_db_gom$prop_obis_in_gom[summary_richness_per_db_gom$taxon_name == "Porifera"]*100)`% complete for sponges to `r format_output(summary_richness_per_db_gom$prop_obis_in_gom[summary_richness_per_db_gom$taxon_name == "Mollusca"]*100)`% for molluscs. However, these levels drop significantly if we consider species for which museum specimens are available from  `r format_output(summary_richness_per_db_gom$prop_idigbio_in_gom[summary_richness_per_db_gom$taxon_name == "Mollusca"]*100)`% for molluscs to `r format_output(summary_richness_per_db_gom$prop_idigbio_in_gom[summary_richness_per_db_gom$taxon_name == "Annelida"]*100)`% for annelids. Similar patterns can be observed for the Pacific Northwest, but overall the levels of data availability are lower: from `r format_output(summary_richness_per_db_koz$prop_obis_in_pnw[summary_richness_per_db_koz$taxon_name == "Porifera"]*100)`% for sponges to `r format_output(summary_richness_per_db_koz$prop_obis_in_pnw[summary_richness_per_db_koz$taxon_name == "Annelida"]*100)`% for annelids for the proportion of species that have records in OBIS, and from  `r format_output(summary_richness_per_db_koz$prop_idigbio_in_pnw[summary_richness_per_db_koz$taxon_name == "Porifera"]*100)`% for sponges to `r format_output(summary_richness_per_db_koz$prop_idigbio_in_pnw[summary_richness_per_db_koz$taxon_name == "Mollusca"]*100)`% for molluscs for the proportion of species that have records in iDigBio.

@@

We combined `r nrow(idigbio_records)` museum records for marine invertebrates collected in the EEZ waters of the continental US representing `r length(unique(tolower(idigbio_records[["data.dwc:phylum"]])))` phyla and `r length(unique(idigbio_records$worms_valid_name))` species. Most samples were collected on the continental shelf (Fig. \@ref(fig:map-diversity-sampling)A). For the East coast, species richness is the highest in South Florida but it is relatively uniform along the coastline. For the West coast, the Salish Sea, the Bay Area, and Southern California have the highest richness (Fig. \@ref(fig:map-diversity-sampling)B).

@@

The inadequacy of the sampling effort compared to the diversity of the fauna is also reflected by the fact that `r prop_singleton_species`% of the species are known from a single record. The strong correlation between the number of samples collected and the species richness suggests that any new sampling effort will lead to new observations (Fig. \@ref(fig:map-diversity-sampling)) and new species. Another indication of this inadequacy is the relation between the number of collected specimen and the number of species recorded through time (Fig. \@ref(fig:idigbio-through-time)). Initial explorations in the late ninetieth century lead to an initial exponential growth in the knowledge of the fauna, that tapered off, until the 1970's when intensive collecting efforts led to an increase in the recording of new taxa (Fig. \@ref(fig:idigbio-through-time)). Since then, the slowing down of collections in the 1970 has been accompanied with a slowing down in the discovery of new records: `r n_spp_comparison$n_spp_2017_2000` species have been documented for the first time since 2000 (`r format_output(n_spp_comparison$n_spp_2017_2000/18)` species.year^-1^), while `r n_spp_comparison$n_spp_1970_1960` have been documented between 1960 and 1970 (`r format_output(n_spp_comparison$n_spp_1970_1960/11)` species.year^-1^). Coordinated large-scale biodiversity expeditions can produce a wealth of data and new records. For instance, a recent study in Western Australia reported that 135 samples led to 805 species of crustaceans and polychaetes, 94.6% and 72% of which were undescribed [@Poore2014].

@@

Modeling the geographic distributions of species, and how they can be impacted by global change has undergone important advances recently. However, it is generally recognized that to obtain reliable results such efforts require to have accurate geographic information for a minimum of 10 specimens but having at least 30 is preferred. Based on iDigBio data, `r prop_10_specimens_species`% of species have less than 10 specimens and `r prop_30_specimens_species`% have less than 30 specimens. This suggests that our understanding of the geographic range of species is limited as most species are known from only a few locations, while efforts to estimate their current and future ranges based on occurrence data are rendered moot by the low number of data points available.

There are important discrepancies in our level of knowledge across phyla. While larger, and accessible groups represent the bulk of the records for marine invertebrates in museum collections, the small organisms, including representatives of the meiofauna are virtually absent. Of the `r n_idigbio_phyla` phyla occurring in iDigBio, `r records_rare_phyla$n_rare_phyla` are represented by less than 500 records, and make up `r records_rare_phyla$prop_rare_phyla`% of the total number of records.

@@

### Genetic data for the future of biodiversity discovery and monitoring

Since its introduction in the early 2000's, DNA barcoding, the sequencing of a common locus across taxa bearing species-specific information, has revitalized taxonomy by facilitating species delineation [@Meyer2005-plos]. More recently, advances in high-throughput sequencing technologies have enabled the parallel sequencing of thousands of species that occur in environmental samples [@Leray2015]. This approach opens up new research venues as it becomes possible to estimate the diversity from species-rich samples that were virtually inaccessible before. This is particularly true in marine communities that include multiple phyla and organisms varying in size by order of magnitude, making identification challenging. However, the utility of the data generated by these projects is enhanced by the possibility of matching DNA sequences obtained to previously sequenced and correctly identified species [@Leray2015]. With decreasing sequencing costs, and the prospect of automating sample collection, these technologies may soon be used routinely to monitor biodiversity [@Bohan2017]. DNA barcoding provides the possibility to link these newly generated data with historical natural history knowledge about species and their distributions. However, the insights we will gain from these approaches are only going to be as good as the level of completeness and accuracy of the information included in reference databases.

@@

Using the fraction of known species that have a barcode as a yard stick of the progress made is not sufficient. Many marine invertebrate species are known to be cryptic complexes that are not as widely distributed as currently reported [@Knowlton2000,@Meyer2005-evolution]. Therefore specimens identified under the same species but sampled in distant locations, could represent cryptic species. Geographic information is missing for most records (`r format_output(100*stat_bold$p_no_coords)`% of the `r format(stat_bold$n_total_records)` BOLD records analyzed here have no geographic coordinates information associated with them). It is thus crucial to ensure that accurate geographic information is provided when DNA barcodes are published, and that enough samples for each species are sequenced, to capture more accurately their geographic range and the extent of their genetic diversity. This cryptic diversity is also at least partially reflected in the fact that `r stat_bold$n_spp_multi_bin` species out of `r stat_bold$n_spp` include more than 1 BIN (BOLD Index Number, operational taxonomic units that closely resemble species [@Ratnasingham2013]).

@@

Based on the results of this study, we recommend a multi-level approach to not only improve the quality of the existing data, but also to efficiently collect new data.

@@

With data aggregation of natural history collections through initiatives like iDigBio, and the compilation of a nearly complete register of marine species with WoRMS, in combination with the development of algorithms for text manipulation, it is increasingly easier to validate and spell check the scientific names of the identifications of museum specimens. Linking species names to identifiers in taxonomic databases would facilitate data linking, specimen discoverability, and data usability. Additionally, because species names registers like WoRMS link the history of the names and their synonymies, it is possible to dissociate the concepts of species identification with the concept of species identity, allowing researchers to compare specimens identified at different time periods, a tedious process that would have required expert knowledge in the past.

@@

### Collect better data faster

@@

Coupling these more traditional approaches of biodiversity documentation with metabarcoding is a promising approach to screen an habitat for its potential for species that do not yet occur in public databases. Metabarcoding can complement and take advantage of the DNA barcodes already available. Additionally, in the future, data generated by metabarcoding efforts can be re-interpreted as more DNA barcodes associated with correctly identified specimens become available. Building the library of DNA barcodes in parallel of metabarcoding efforts ensures that matches in the database will correspond to actual specimens deposited in natural history collections; ruling out possible artifacts of the method. Information about species identity and distribution will thus build on existing natural history data rather than being limited to matching DNA sequences across studies.

@@

>>>>

Museum collections have been recording our knowledge about species and their geographic ranges, but until recently, this information was fragmented across institutions and difficult to synthesize. The digitization of natural history collections and other biodiversity information systems can now be used to enable synthesis and highlight knowledge gaps. Here we use these data to synthesize the state of our knowledge for marine invertebrates in the continental US. We show that current knowledge and sampling efforts are inadequate given the diversity of the fauna and the geographic extent of US. While recent high-throughput sequencing technologies promise to greatly speed up the documentation of marine species and their ranges, its value would be greatly improved by anchoring the results into existing DNA sequence data and associated vouchers. However, the best documented phyla have at most 25% of their species sequenced for the most widely used DNA barcoding gene, cytochrome oxidase I (COI). More sampling, coordinated at the scale of the US, is needed to improve our knowledge of species and their geographic ranges. This data is needed to detect the impact of climate changes and other anthropogenic strains to global environments. Advances in computing, information systems, and sequencing technologies, have set the stage to inform where future efforts for documenting biodiversity should be applied.

@@

With increasing impact of human activities on the biosphere, we need efficient and accurate approaches to document changes in species ranges and community composition. While terrestrial ecosystems have received considerable attention, the baseline of healthy and resiliency of marine ecosystems are not well understood [@Worm2006], and modeling the impact of human activities is limited to a few taxonomic groups [@Tittensor2010]. A major hindrance for marine species, due to their complex life history strategies, and their size range, is that we do not have enough information about which species live where, or what portion of marine biodiversity remains to be discovered and described [@Mora2011]. Additionally, coordinated marine ecosystem monitoring initiatives are lacking [@Duffy2013,@Borja2016]. There is therefore a pressing need to improve our knowledge of marine systems before species go extinct, and their functioning is irreversibly altered.

Until very recently, our knowledge of biodiversity was scattered among heterogeneous sources (e.g. natural history collections, publications, expert knowledge), difficult to access, and therefore difficult to synthesize. The development of public databases for natural history records (e.g. iDigBio [@Page2015]), species occurrences (e.g., OBIS [@Zhang2002]), genetic data (e.g., GenBank [@Benson2013], BOLD [@Ratnasingham2007a]), and registers of species names (e.g., WoRMS [@Costello2013b]), now allow us to evaluate what and how much we know. Here, we aggregate publicly available data for marine invertebrates that occur within the limits of the exclusive economic zone (EEZ) of the continental United States, as well as the Gulf of Mexico and the Pacific Northwest, to highlight gaps in our knowledge that provide a roadmap for important new directions of global research. We show that public databases are relatively incomplete, and that most species are known from only a few specimens and a few locations. We emphasize that our understanding of marine biodiversity, and the impact of human activities on communities require not only to get a more accurate list of the species that inhabits the oceans, but we also need more comprehensive data on species distributions and abundances. This can only be achieved with additional cost-effective sampling and a commitment to training more taxonomists and experts that can identify and interpret the material collected.

@@

To compare the faunistic lists from the Gulf of Mexico and the Pacific Northwest with records in public databases, we queried the iDigBio (https://portal.idigbio.org) and OBIS (http://www.iobis.org/) databases for all records they included in the same geographic boundaries as the lists. After filtering these lists to only include the same higher taxonomic level taxa as the species lists, and keeping only records for which the species could be matched to a species name in WoRMS, we had for the Gulf of Mexico `r format(nrow(idigbio_gom_records), big.mark=",")` and `r format(nrow(obis_gom_records), big.mark=",")` records for iDigBio and OBIS respectively, representing `r format(dplyr::n_distinct(idigbio_gom_records$worms_valid_name), big.mark=",")` and `r format(dplyr::n_distinct(obis_gom_records$worms_valid_name), big.mark=",")` species. For the Pacific Northwest, we retrieved `r format(nrow(idigbio_pnw_records), big.mark=",")` and `r format(nrow(obis_kozloff_records), big.mark=",")` records for iDigBio and OBIS respectively representing `r format(dplyr::n_distinct(idigbio_pnw_records$worms_valid_name), big.mark=",")` and `r format(dplyr::n_distinct(obis_kozloff_records$worms_valid_name), big.mark=",")` species. For the Gulf of Mexico, the majority of the species included in the expert lists are recorded in both iDigBio and OBIS (`r format_output(species_in_common$n_spp_gom_idigbio_obis/species_in_common$n_spp_gom*100)` %), or only OBIS (`r format_output(species_in_common$n_spp_gom_obis/species_in_common$n_spp_gom*100)` %) (Fig. \@ref(fig:database-overlap)). For the Pacific Northwest, these proportions were much lower with only `r format_output(species_in_common$n_spp_kozloff_idigbio_obis/species_in_common$n_spp_kozloff*100)`% of the species from the regional list with records in OBIS and iDigBio, and `r format_output(species_in_common$n_spp_kozloff_obis/species_in_common$n_spp_kozloff*100)`%  in OBIS only (Fig. \@ref(fig:database-coverage)).

```{r compare_database_coverage, fig.cap='Overlap between the regional species list (list), records in iDigBio (idigbio), records in OBIS (obis), and records in BOLD (bold) for the Gulf of Mexico (left) and the Pacific Northwest (right). (\\#fig:database-coverage)', echo=FALSE}
knitr::include_graphics("figures/database_coverage.pdf")
```

@@

We extracted `r format(sum(gom_worms$is_marine, na.rm = TRUE), big.mark=",")` marine invertebrates species from the faunistic list of the Gulf of Mexico, and `r format(sum(kozloff_worms$is_marine, na.rm=TRUE), big.mark=",")` species from the Pacific Northwest. We then looked for the number of species listed that are known to occur in the same geographic area, the United States, or anywhere else in the world. Overall, OBIS had georeferenced records for most of the species that are included in the species lists. However, even for the better studied phyla about 75% of the species have records from the same geographic area, while it is less than 50% for the Pacific Northwest.

@@

These results suggest that even when considering species lists that have been curated and that represent possibly the most accurate knowledge for any particular geographic area, today we can only partially reconstruct these lists based on digitized information. For instance, based on OBIS data the list would be `r format_output(summary_richness_per_db_gom$prop_obis_in_gom[summary_richness_per_db_gom$taxon_name == "Porifera"]*100)`% complete for sponges to `r format_output(summary_richness_per_db_gom$prop_obis_in_gom[summary_richness_per_db_gom$taxon_name == "Mollusca"]*100)`% for molluscs. However, these levels drop significantly if we consider species for which museum specimens are available from  `r format_output(summary_richness_per_db_gom$prop_idigbio_in_gom[summary_richness_per_db_gom$taxon_name == "Mollusca"]*100)`% for molluscs to `r format_output(summary_richness_per_db_gom$prop_idigbio_in_gom[summary_richness_per_db_gom$taxon_name == "Annelida"]*100)`% for annelids. Similar patterns can be observed for the Pacific Northwest, but overall the levels of data availability are lower: from `r format_output(summary_richness_per_db_koz$prop_obis_in_pnw[summary_richness_per_db_koz$taxon_name == "Porifera"]*100)`% for sponges to `r format_output(summary_richness_per_db_koz$prop_obis_in_pnw[summary_richness_per_db_koz$taxon_name == "Annelida"]*100)`% for annelids for the proportion of species that have records in OBIS, and from  `r format_output(summary_richness_per_db_koz$prop_idigbio_in_pnw[summary_richness_per_db_koz$taxon_name == "Porifera"]*100)`% for sponges to `r format_output(summary_richness_per_db_koz$prop_idigbio_in_pnw[summary_richness_per_db_koz$taxon_name == "Mollusca"]*100)`% for molluscs for the proportion of species that have records in iDigBio.

@@

We combined `r format(nrow(idigbio_records), big.mark=",")` museum records for marine invertebrates collected in the EEZ waters of the continental US representing `r length(unique(tolower(idigbio_records[["data.dwc:phylum"]])))` phyla and `r format(length(unique(idigbio_records$worms_valid_name)), big.mark=",")` species. Most samples were collected on the continental shelf (Fig. \@ref(fig:map-diversity-sampling)A). For the East coast, species richness is the highest in South Florida but it is relatively uniform along the coastline. For the West coast, the Pacific Northwest, the San Francisco Bay Area, and Southern California have the highest richness (Fig. \@ref(fig:map-diversity-sampling)B).

@@

The inadequacy of the sampling effort compared to the diversity of the fauna is also reflected by the fact that only `r prop_singleton_species`% of the species are known from a single record. The strong correlation between the number of samples collected and the species richness suggests that any new sampling effort will lead to new observations (Fig. \@ref(fig:map-diversity-sampling)) and new species. Another indication of this inadequacy is the relation between the number of collected specimen and the number of species recorded through time (Fig. \@ref(fig:idigbio-through-time)). Initial explorations in the late ninetieth century lead to an initial exponential growth in the knowledge of the fauna, that tapered off, until the 1970's when intensive collecting efforts led to an increase in the recording of new taxa (Fig. \@ref(fig:idigbio-through-time)). Since then, the slowing down of collections after the 1970s has been accompanied with a slowing down in the discovery of new records: `r n_spp_comparison$n_spp_2017_2000` species have been documented for the first time since 2000 (`r format_output(n_spp_comparison$n_spp_2017_2000/18)` species.year^-1^), while `r n_spp_comparison$n_spp_1970_1960` have been documented between 1960 and 1970 (`r format_output(n_spp_comparison$n_spp_1970_1960/11)` species.year^-1^). Therefore, coordinated large-scale biodiversity expeditions will continue to generate a wealth of data and new records. For instance, a recent study in Western Australia reported that 135 samples led to 805 species of crustaceans and polychaetes, 94.6% and 72% of which were undescribed [@Poore2014].

@@

Predicting the geographic range of species, and how they can be impacted by global change has undergone important advances recently. However, it is generally recognized that to obtain reliable results such efforts require to have accurate geographic information for a minimum of 10 specimens but having at least 30 is preferred. Based on iDigBio data, `r prop_10_specimens_species`% of species have less than 10 specimens and `r prop_30_specimens_species`% have less than 30 specimens. This suggests that our understanding of the geographic range of species is limited as most species are known from only a few locations, while efforts to estimate their current and future ranges based on occurrence data are rendered moot by the low number of data points available.

Furtheremore, there are important discrepancies in our level of knowledge across phyla. While larger, and accessible groups represent the bulk of the records for marine invertebrates in museum collections, the small organisms, including representatives of the meiofauna are virtually absent. Of the `r n_idigbio_phyla` phyla occurring in iDigBio, `r records_rare_phyla$n_rare_phyla` are represented by less than 500 records, and make up `r records_rare_phyla$prop_rare_phyla`% of the total number of records.

<!-- From Mark: These previously undersampled taxa are likely to be much more important for the detection of subtle changes in environmental quality due to their size and physiological vulnerability. (?).  -->
<!-- also, the impact of changes in the composition in their communties is largely unexplored, look into Bik's paper? -->

@@

### Molecular data for the future of biodiversity discovery and monitoring

Since its introduction in the early 2000's, DNA barcoding, the sequencing of a common locus across taxa bearing species-specific information, has revitalized taxonomy by facilitating species delineation [@Meyer2005-plos]. More recently, advances in high-throughput sequencing technologies have enabled the parallel sequencing of thousands of species that occur in environmental samples cost effectively [@Leray2015]. This approach opens up new research venues as it becomes possible to estimate the diversity from species-rich samples that were virtually inaccessible before. This is particularly true in marine communities that include multiple phyla and organisms varying in size by order of magnitude, making identification challenging. However, the utility of the data generated by these projects is enhanced by the possibility of matching DNA sequences obtained to previously sequenced and correctly identified species [@Leray2015]. With decreasing sequencing costs, and the prospect of automating sample collection, these technologies may soon be used routinely to monitor biodiversity at defined temporal frequency [@Bohan2017]. DNA barcoding provides the possibility to link these newly generated data with historical natural history knowledge about species and their distributions. However, the insights we will gain from these approaches are only going to be as good as the level of completeness and accuracy of the information included in reference databases.

@@

Using the fraction of known species that have a barcode as a yard stick of the progress made is not sufficient. Many marine invertebrate species are known to be cryptic complexes that are not as widely distributed as currently reported [@Knowlton2000,@Meyer2005-evolution]. Therefore specimens identified under the same species but sampled in distant locations, could represent cryptic species. Geographic information is missing for most records (`r format_output(100*stat_bold$p_no_coords)`% of the `r format(stat_bold$n_total_records, big.mark=",")` BOLD records analyzed here have no geographic coordinate information associated with them). It is thus crucial to ensure that accurate geographic information is provided when DNA barcodes are published, and that enough samples for each species are sequenced, to capture more accurately their geographic range and the extent of their genetic diversity. This cryptic diversity is also at least partially reflected in the fact that `r stat_bold$n_spp_multi_bin` species out of `r format(stat_bold$n_spp, big.mark=",")` include more than 1 BIN (BOLD Index Number, operational taxonomic units that closely resemble species [@Ratnasingham2013]).

@@

Based on the results of this study, we recommend a multi-level approach for both improving the quality of existing data, as well as for the efficient collection of new data.

@@

With data aggregation of natural history collections through initiatives like iDigBio, and the compilation of a nearly complete register of marine species with WoRMS, in combination with the development of algorithms for text analysis, it is increasingly easier to validate and spell check the scientific names of the identifications of digitized museum specimens. Linking species names to identifiers in taxonomic databases would facilitate data linking, specimen discoverability, and data usability. Additionally, because species names registers like WoRMS link the history of the names and their synonymies, it is possible to dissociate the concepts of species identification with the concept of species identity, allowing researchers to compare specimens identified at different time periods, a tedious process that would have required expert knowledge in the past.

@@

### Collect better data faster and more cost effectively

@@

Coupling these more traditional approaches of biodiversity documentation with metabarcoding is a promising approach to screen an habitat for its potential for species that do not yet occur in public databases. <!-- explain why better --> Metabarcoding can complement and take advantage of the DNA barcodes already available. Additionally, in the future, data generated by metabarcoding efforts can be re-interpreted as more DNA barcodes associated with correctly identified specimens become available. Building the library of DNA barcodes in parallel of metabarcoding efforts ensures that matches in the database will correspond to actual specimens deposited in natural history collections; ruling out possible artifacts of the method. Information about species identity and distribution will thus build on existing natural history data rather than being limited to matching DNA sequences across studies.

@@

## Material and methods

### Data sources

iDigBio:
OBIS:
WoRMS:
